Reading Notes

### 2020-09-03 abstract.tex
send to undergrads next

In this research we will use molecular simulations to predict the active layer morphologies for combinations of chemistries and how they contribute to device efficiency.
Connecting electronic processes like charge transport with larger length scales of active layer morphology demands simulation workflows between tools which has exposed significant interoperability challenges.
We propose developing new simulation infrastructure that solves longstanding problems with simulation management, transferability, reproducibility, usability, and extensibility.
Specifically, we develop tools in the Molecular Simulation Design Framework (MoSDeF) for automating the coarse-graining of OPV chemistries and predicting and analyzing equilibrated OPV morphologies.

>>>>

In this research we will use molecular simulations to predict the active layer morphologies for combinations of chemistries and how they contribute to device efficiency.
Connecting electronic processes like charge transport with larger length scales of active layer morphology demands simulation pipelines, which have exposed significant challenges to software interoperability.
We propose developing new simulation infrastructure that solves these longstanding problems with simulation management.
Specifically, we develop tools in the Molecular Simulation Design Framework (MoSDeF) for automating the coarse-graining of OPV chemistries and predicting and analyzing equilibrated OPV morphologies.
